### 2013-11-28 manuscripts/reply/reply-main.tex
Working on reply ms.
Working on section covering the theory of empirical Bayesian
model choice.

\subsection*{Theoretical implications of empirical priors for Bayesian model
choice}
\begin{linenomath}
Bayesian inference is a method of inductive learning in which Bayes' rule is
used to update our beliefs about a model $M$ as new information becomes
available.
If we let \allParameterValues represent the set of all possible parameter
values for model $M$, we can define a prior distribution for all $\theta \in
\allParameterValues$ such that $p(\theta \given M)$ describes our belief that
any given \myTheta{} is the true value of the parameter.
If we let \allDatasets represent all possible datasets then we can 
define a sampling model for all $\theta \in
\allParameterValues$ and $\alignment{}{} \in \allDatasets$ such that
$p(\alignment{}{} | \theta, M)$ measures our belief that any dataset \alignment{}{}
will be generated by any state \myTheta{} of model $M$.
After collecting a new dataset \alignment{i}{}, we can use Bayes' rule to
calculate the posterior distribution
\begin{equation}
    p(\myTheta{} \given \alignment{i}{}, M) = \frac{p(\alignment{i}{} \given
    \myTheta{}, M)p(\myTheta{}, M)}{p(\alignment{i}{} \given M)},
    \label{eq:bayesrule}
\end{equation}
where
\begin{equation}
    p(\alignment{i}{} \given M) = \int_{\myTheta{}} p(\alignment{i}{} \given
    \myTheta{}, M)p(\myTheta{} \given M) d\myTheta{}
    \label{eq:marginallikelhiood}
\end{equation}
is the marginal likelihood of the model.
The posterior distribution is a measure of our beliefs after seeing the new
information.
\end{linenomath}

@@

However, if we look at Equation~\ref{eq:bayesmodelchoice}, we see that in
Bayesian model choice it is now the \emph{marginal} likelihood of a model the
updates the prior to yield the model's posterior probability.
Thus the integral over the entire parameter space of the likelihood weighted by
the prior probability density is no longer a normalizing constant, but rather
is what informs the posterior probability of that model from the data.
As a result, Bayesian model choice tends to be much more sensitive to priors
than Bayesian parameter estimation.

Another important difference of Bayesian model choice illustrated by
Equation~\ref{eq:bayesmodelchoice} is that the value of interest, the
posterior probability of a model, is not a function of \myTheta{}, because
it is integrated out of the marginal likelihoods of the candidate models.
Thus, unlike parameter estimates, the estimated posterior probability of a
model is a single value (rather than a distribution) lacking a measure of
posterior uncertainty, and in most cases has no true value.
In most empirical applications, we know all candidate models are incorrect, but
our goal is to summarize the relative probabilities that they could produce the
observed data.
Model posterior probabilities are inherently measures of our belief in the
models after our prior beliefs are updated by the data being analyzed.

This complicates the meaning of model posterior probabilities when Bayes' rule
is violated by empirically informing priors.
For empirical Bayesian parameter estimation, the objective is that by giving the
data more weight relative to the prior, the posterior distribution will be
peaked near the true value(s) of the model's parameter(s).
There is no such justification for empirical Bayesian model choice, because
there are no true values for the model probabilities being estimated.
Using the data twice will simply mislead our posterior beliefs in the models
being compared.

These distinctions between Bayesian parameter estimation and model choice can
be illustrated with a simple example.
Let us say we are interested in the probability of a particular coin being
weighted toward landing heads (i.e., $p(p(heads) > 0.5)$).
We already have data from flipping a different coin 20 times that landed both
heads and tails 10 times, and so we decide to use these data in specifying a
beta prior on fairness of the new coin of $beta(a=10, b=10)$
(Figure~\ref{figCoinFlip}).
We collect data by flipping the coin $N=10$ times, $y=3$ of which land heads.
Given the beta distribution is a conjugate prior for a binomial likelihood, the
posterior distribution has the nice analytical form $\theta \given y,N \sim
beta(a + y, b + N - y)$, which for the new dataset is simply $beta(13, 17)$;
this is the true posterior distribution of $\theta$ given our prior information
and data (Figure~\ref{figCoinFlip}).
Thus, the posterior mode estimate of the probability of heads is 0.429, and the
posterior probability of our hypothesis is then $p(p(heads) > 0.5 \given
heads=3, N=10) = 0.23$.
To give the data more weight relative to the prior, we could use it twice, and
calculate an empirical Bayes estimate using a prior of $beta(13,17)$.  This
results in a distribution of $beta(16, 24)$ (Figure~\ref{figCoinFlip}), with a
mode of 0.395, and the $p(p(heads) > 0.5 \given heads=3, N=10) = 0.10$.
Whereas the estimate of the parameter $p(heads)$ is a distribution, the mode of
which changed only 8\% under the empirically informed prior, the posterior
probability of our model of interest ($p(p(heads) > 0.5)$) is a single value,
which changed by 56\% under the empirical prior.
From this example, we can see how Bayesian model choice is more sensitive
to priors, and how using the data twice can mislead the posterior
probability of a model in light of new data.

>>>>

\subsection*{Theoretical implications of empirical priors for Bayesian model
choice}
\begin{linenomath}
Bayesian inference is a method of inductive learning in which Bayes' rule is
used to update our beliefs about a model $M$ as new information becomes
available.
If we let \allParameterValues represent the set of all possible parameter
values for model $M$, we can define a prior distribution for all $\theta \in
\allParameterValues$ such that $p(\theta \given M)$ describes our belief that
any given \myTheta{} is the true value of the parameter.
If we let \allDatasets represent all possible datasets then we can 
define a sampling model for all $\theta \in
\allParameterValues$ and $\alignment{}{} \in \allDatasets$ such that
$p(\alignment{}{} | \theta, M)$ measures our belief that any dataset \alignment{}{}
will be generated by any state \myTheta{} of model $M$.
After collecting a new dataset \alignment{i}{}, we can use Bayes' rule to
calculate the posterior distribution
\begin{equation}
    p(\myTheta{} \given \alignment{i}{}, M) = \frac{p(\alignment{i}{} \given
    \myTheta{}, M)p(\myTheta{} \given M)}{p(\alignment{i}{} \given M)},
    \label{eq:bayesrule}
\end{equation}
where
\begin{equation}
    p(\alignment{i}{} \given M) = \int_{\myTheta{}} p(\alignment{i}{} \given
    \myTheta{}, M)p(\myTheta{} \given M) d\myTheta{}
    \label{eq:marginallikelhiood}
\end{equation}
is the marginal likelihood of the model.
The posterior distribution is a measure of our beliefs after seeing the new
information.
\end{linenomath}

@@

However, if we look at Equation~\ref{eq:bayesmodelchoice}, we see that in
Bayesian model choice it is now the \emph{marginal} likelihood of a model that
updates the prior to yield the model's posterior probability.
Thus the integral over the entire parameter space of the likelihood weighted by
the prior probability density is no longer a normalizing constant, but rather
is what informs the posterior probability of that model from the data.
As a result, Bayesian model choice tends to be much more sensitive to priors
than Bayesian parameter estimation.
In other words, the Bayesian model choice is much more sensitive to the marginal
likelihood of models than parameter estimation.
Whereas parameter estimation will tend to succeed if the topography of the
likelihood surface is captured regardless of scale, model choice must compare
the average height of this surface between models.

Another important difference of Bayesian model choice illustrated by
Equation~\ref{eq:bayesmodelchoice} is that the value of interest, the
posterior probability of a model, is not a function of \myTheta{}, because
it is integrated out of the marginal likelihoods of the candidate models.
Thus, unlike parameter estimates, the estimated posterior probability of a
model is a single value (rather than a distribution) lacking a measure of
posterior uncertainty.
Also, unlike model parameters, the posterior probabilities of candidate
models have no clear true values.
In most applications, we know all candidate models are incorrect, but our goal
is to summarize the relative probabilities that they could produce the observed
data.
Thus, model posterior probabilities are inherently measures of our belief in the
models after our prior beliefs are updated by the data being analyzed.

This complicates the meaning of model posterior probabilities when Bayes' rule
is violated by empirically informing priors.
For empirical Bayesian parameter estimation, the objective is that by giving the
data more weight relative to the prior, the posterior distribution will be
peaked near the true value(s) of the model's parameter(s).
There is no such justification for empirical Bayesian model choice, because
there are no true values for the model probabilities being estimated.
By using the data twice, we fail to account for prior uncertainty and mislead
our posterior beliefs in the models being compared; we will be over confident
in some models and under confident in others.

These distinctions between Bayesian parameter estimation and model choice can
be illustrated with a simple example.
Let us say we are interested in the fairness of a particular coin, and we
denote the probability of landing heads as \myTheta{}.
More specifically, we are interested in the probability of two models, $M_1$
and $M_2$.
In both models the outcomes of flipping the coin are assumed to be binomially
distributed, but under $M_1$ the coin is weighted toward landing heads (i.e.,
$\myTheta{} > 0.5)$), where as under $M_2$, the coin is weighted toward landing
tails (i.e., $\myTheta{} < 0.5$).
We already have data from flipping a different coin 20 times that landed both
heads and tails 10 times, and so we decide to use these data in specifying a
beta prior on fairness of the new coin of $beta(a=10, b=10)$
(Figure~\ref{figCoinFlip}).
We collect data by flipping the coin $N=10$ times, $y=3$ of which land heads.
Given the beta distribution is a conjugate prior for a binomial likelihood, the
posterior distribution has the nice analytical form $\theta \given y,N \sim
beta(a + y, b + N - y)$, which for the new dataset is simply $beta(13, 17)$
(Figure~\ref{figCoinFlip}).
The posterior mode estimate of the probability of heads is 0.429, and following
Equation~\ref{eq:marginallikelhiood} the marginal likelihoods of our models of
interest are
\begin{equation}
    p(y=3, N=10 \given M_1) = \int_{0.5}^{1} p(y=3, N=10 \given
    \myTheta{}, M_1)p(\myTheta{} \given M_1) d\myTheta{} \approx 0.029,
\end{equation}
and
\begin{equation}
    p(y=3, N=10 \given M_2) = \int_{0}^{0.5} p(y=3, N=10 \given
    \myTheta{}, M_2)p(\myTheta{} \given M_2) d\myTheta{} \approx 0.097.
\end{equation}
Given the models have equal probability under our prior, and following
Equation~\ref{eq:bayesmodelchoice}, we can calculate the posterior
probability of Model 1 as
\begin{equation}
    p(M_1 \given y=3, N=10) = \frac{p(y=3, N=10 \given M_1)}{p(y=3, N=10 \given
    M_1) + p(y=3, N=10 \given M_2)} \approx 0.23.
\end{equation}
This is the true posterior probability of Model 1 given our prior information
and data.

To give the data more weight relative to the prior, we could use it twice, and
calculate an empirical Bayes estimate using a prior of $beta(13,17)$.  This
results in a distribution of $beta(16, 24)$ (Figure~\ref{figCoinFlip}), with a
mode of 0.395, and $p(M_1 \given y=3, N=10) = 0.10$.
Whereas the estimate of the parameter $p(heads)$ is a distribution, the mode of
which changed only 8\% under the empirically informed prior, the posterior
probability of Model 1 is a single value, which changed by 56\% under the
empirical prior.
This demonstrates how Bayesian model choice is more sensitive to priors than
parameter estimation.
Also, we can see how using the empirically informed prior ignores our prior
uncertainty, leading to an underestimate of our posterior uncertainty
(Figure~\ref{figCoinFlip}), and ultimately misleads us toward overconfidence in
Model 2.
Our mode estimate of \myTheta{} under the empirical prior might be closer
to the true value than our posterior mode.
Let us assume the truth of the matter is that the coin under study has a broad
flat edge, and as a result lands on its edge at a certain frequency.
Hence, both of our models are incorrect (i.e., the outcomes of flipping the
coin are not binomially distributed).
From this example, we can see how Bayesian model choice is more sensitive to
priors, and how using the data twice can mislead the posterior probability of a
model in light of new data.
